---
title: "Defend Your Enemy Against Hate Speech"
author: "Anonymous, Anonymous"
date: "`r Sys.Date()`"
bibliography: ["rpackages.bib", "../Misdoom/bibliography.bib"]
biblio-style: "apalike"
link-citations: true
always_allow_html: yes
output:
  rmdformats::material:
    highlight: kate
    collapsed: false
    dev: png
    self_contained: true
    number_sections: true
    code_folding: hide
    thumbnails: true
    gallery: true
    fig_width: 6
    fig_height: 3.5
    df_print: kable
    use_bookdown: true
  pdf_document:
    fig_caption: true
    keep_tex: true
    latex_engine: xelatex
    citation_package: natbib
    dev: pdf
---

 
```{r setup, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, paged.print=TRUE}
## Global options
library(knitr)
options(max.print = "75")
opts_chunk$set(
  echo = TRUE,
  cache = FALSE,
  prompt = FALSE,
  tidy = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE,
  fig.width = 6,
  fig.height = 3.5,
  fig.retina = 2
)
opts_knit$set(width = 100)

# Load required libraries
library(rmdformats)
library(rmdtemplates)
library(tidyverse)
library(DT)
library(kableExtra)
# add libraries here
pkgs <- c("knitr", "tidyverse", "rmdformats", "kableExtra", "rmdtemplates", "DT")
rmdtemplates::write_bib(pkgs)
```


# Abstract {-}

Both hate speech and disinformation negatively influence the internet's potential for public deliberation and lead to polarization between political groups. In this paper, we examine the potential of counter speech to bolster public deliberation and reduce polarization. In two focus groups, we interview participants on what motivates them to engage in counter speech in general as well as counter speech favoring political adversaries. Firstly, we find a sharp distinction between participants who avoid engaging with hate speech and participants who actively engage with hate speech in order to combat it. Thus, the most important predictor for counter speech favoring adversaries is an individual's propensity for counter speech in general. In turn, motivations for counter speech in general are a strong sense of morality, a perception of the internet as an important space for public deliberation, and a sense of responsibility to enforce rules for a fair debate. Many of those participants view their online activitiy as a form of activism. Additionally, individuals engaging in counter speech hope to positively influence not necessarily the hater, but the broader audience.

```{r introduction, eval=FALSE, child='../Misdoom/10-introduction', include=FALSE}
```
```{r related-work, child='../Misdoom/20_related-work.Rmd'}
```
```{r method, child='../Misdoom/30_method.Rmd', eval = TRUE}
```
```{r results, child='../Misdoom/40_Results.Rmd', eval = TRUE}
```
```{r discussion-and-conclusion, child='../Misdoom/50_discussion-and-conclusion.Rmd'}
```

```{r dummy, child = '../Misdoom/99_dummy.Rmd', eval = FALSE}
```







# Data and Materials
On this sub-page you can find the data used as a downloadable files.

## Materials

You can find the following supplementary materials in the Github Repository:

These documents are in German:

ANONYMIZED 
<!--
* [Focus group guideline](https://github.com/digitalemuendigkeit/misdoom2020/raw/master/supplementarymaterial/Focus-Group-Guide-German.pdf)
* [Slides used in the focus group](https://github.com/digitalemuendigkeit/misdoom2020/raw/master/supplementarymaterial/Focus-Group-Slides-German.pdf)
* [Questionnaire in focus group](https://github.com/digitalemuendigkeit/misdoom2020/raw/master/supplementarymaterial/Questionnaire-German.pdf)
* [Transcript of Group "moderately active"](https://github.com/digitalemuendigkeit/misdoom2020/raw/master/supplementarymaterial/Transcript-Moderately-Active-Group-German.pdf)
* [Transcript of group "very active"](https://github.com/digitalemuendigkeit/misdoom2020/raw/master/supplementarymaterial/Transcript-Very-Active-Group-German.pdf)
* [Transcription system](https://github.com/digitalemuendigkeit/misdoom2020/raw/master/supplementarymaterial/Transcription-System-German.pdf)

You can also directly see all suppl. materials in the [github repository](https://github.com/digitalemuendigkeit/misdoom2020/tree/master/supplementarymaterial).
-->

## Data of participants

```{r data_1, echo=TRUE, message=TRUE, warning=TRUE, paged.print=TRUE}
data_df <- read.csv(file = "../data/participants.csv",header = TRUE,sep = ";",quote = "",dec = ",", fill = TRUE, nrows = 11, )


datatable(data_df, filter = list(position = 'top', clear = TRUE, plain = FALSE), extensions = c('Buttons','FixedColumns'), options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf'),
    scrollX = TRUE,
    fixedColumns = TRUE
  ))

```   



```{r r_citations2, eval=TRUE, include=TRUE, results="asis"}
#rmdtemplates::line_cite(pkgs) # This creates a single line citing all packages
rmdtemplates::list_cite(pkgs) # This creates a "thightlist" of all packages 
```


```{r acks, child='../Misdoom/90_acks.Rmd', eval = FALSE}
```

# References
